### 2019-03-14 proposals/TESS_GI_cycle02/tessgi_gully_cycle2.tex
Writing prose for the proposal

\subsection{Starspots as confounders of isochronal ages}
Provide text and figures that justify the scientific need for \tess\ observations and analyses here.
Justify your choice of cadence. When applicable, justify your choice of new 2 min cadence observations.
If your program includes theoretical, simulation, or ground-based observing components (limited to no
more than 30\% effort), describe why these efforts are critical in addition to \tess\ observations.

For example, see \cite{2015ApJ...807..174S} and \cite{2015arXiv150706460F}).  Specifically, stellar evolution models

@@

\subsection{Transit light source effect}
thinga

@@

\subsection{Probabilistic lookup table for spot temperature and spot coverage}
\subsection{Direct estimate of spot coverage for selected high value targets}
\subsection{Gateway to future investigation pathways}
\subsubsection{Trends in spot coverage with lightcurve periodic substructure}
\subsubsection{Trends in spot coverage with lightcurve high frequency residual substructure}
\subsubsection{Trends in spot coverage with lightcurve high frequency residual substructure}

@@

MGS will carry out the data analysis using custom scripts that build upon the heritage of the Kepler data analysis ecosystem, including \texttt{lightkurve}, \texttt{astropy}, \texttt{celerite}, \texttt{BombScargle}, and \texttt{bokeh}.  MGS will first apply these scripts to Kepler SAP lightcurves or detrended K2 data while in his current role as support scientist at the Kepler/K2 Guest Observer Office.  MGS will adapt and apply these scripts to TESS data---in the event of GI proposal selection---starting in Fall 2019.  All scripts will be publicly available and developed openly on GitHub, including tutorial Jupyter Notebooks.  MGS will produce an interactive \texttt{bokeh} tool to visualize the Fourier decomposition of a periodic lightcurve into its constituent components.  This tool will leverage the PI's familiarity with \texttt{bokeh}, to aid students' visualization different amplitudes.  A machine readable database will be produced that contains the following information for each star found to possess starspot-induced lightcurve modulation: 1) the period, 2) an iteratively determined mask of stellar flares and/or spurious data artifacts, 3) a vector of Chebychev polynomial coefficients to account for any long-term normalization trends on timescales comparable to the observation window, and 4) a vector of Fourier amplitudes that can reconstruct the periodic structures in the lightcurve to within the signal-to-noise ratio of the data.

>>>>

\subsection{Starspots as confounders of isochronal ages}
For example, see \cite{2015ApJ...807..174S} and \cite{2015arXiv150706460F}).  Specifically, stellar evolution models

@@

\subsection{Transit Light Source Effect}
The diminution of flux arising from occultations of the stellar disk contains information about the relative sizes of the occulting bodies.  A commonsense exoplanet heuristic dictates that the relative transit depth $D$ (in units of ppm or $\%$) equals the ratio of the bodies' projected areas ($R_p^2/R_\star^2$).  Addtional correction factors account for limb darkening \citep{2002ApJ...580L.171M}.  Starspots on a stellar surface can exhibit spatial segrations\footnote{Sunspots reside on the Sun's mid-latitudes, and starspots can exist near the stellar poles, as evinced in spatially resolved interferometry of nearby giant stars \citep{2016Natur.533..217R}} that yield \emph{unocculted starspots}: spots that are present on the surface but are not traversed during event during transit.  These unocculted starspots confound the mapping of transit depth to planet radius: a planet ``looks bigger'' in a transit depth if it blocks the brighter-on-average flux of the stellar disk.  \textbf{You cannot measure a planet radius without making some assumptions about the extent, contrast, and distribution of starspots.}

The prevailing assumptions within the exoplanet community has been that starspot covering fractions are small enough that the

@@

\subsection{Probabilistic lookup table for spot temperature and spot coverage}
The probabilistic lookup table for spot temperature and filling factor will empower exoplanet researchers to constrain biases in exoplanet transit radii.

\subsection{Direct estimate of spot coverage for selected high value targets}
The spectroscopic analysis component of this work will add long-term value to the TESS legacy.

\subsection{Trends in spot coverage with lightcurve periodic substructure}
The adopted Fourier analysis technique naturally collates the relative amplitudes of periodic structures, which encode some additional information about the spatial distribution of stellar surface inhomogeneities, and/or differential rotation.  The collated harmonics will enable exploratory analyses of trends with other observables, as recently proposed in the amount of time a spot-modulated \kepler\ lightcurve exhibits single or double dips \citep{2018ApJ...863..190B}.

@@

The Pincipal Investigator (PI) will carry out the data analysis using custom scripts that build upon the heritage of the Kepler data analysis ecosystem, including \texttt{lightkurve}, \texttt{astropy}, \texttt{celerite}, \texttt{BombScargle}, \texttt{PyTorch}, and \texttt{bokeh}.  The PI will first apply these scripts to Kepler/K2 lightcurves while in their current role as support scientist at the Kepler/K2 Guest Observer Office.  The PI will relocate to the University of Texas at Austin in February 2020 as a Research Fellow.  UT Austin undergraduate and graduate students will lead the application of TESS-adapted scripts to \tess\ FFI lightcurves.  \tess-adapted scripts will leverage \texttt{TESS-cut} and \texttt{elenor} to produce lightcurves from FFIs.  Half of the funding will go to summer 2020 student salaries, and half will go to support the PI.  All reproducible scripts---including Jupyter Notebook tutorials---will be publicly available and developed openly on GitHub.  MGS will provide students with an interactive \texttt{bokeh} tool to visualize the Fourier decomposition of a periodic lightcurve into its constituent components.  This tool will leverage the PI's familiarity with \texttt{bokeh} to aid understanding and rapid visual spotchecking of the multidimensional analysis output.  Finally, a High Level Science Product (HLSP) will be delivered to MAST that contains the following information for each star found to possess detectable starspot-induced lightcurve modulation: 1) the period or periods, 2) an iteratively determined outlier mask of stellar flares, occultations, or spurious data artifacts, 3) a vector of Chebychev polynomial coefficients to account for any long-term normalization trends on timescales comparable to the observation window, and 4) an $N_{\mathrm{Fourier}}$ vector of Fourier harmonic amplitudes that reconstruct the periodic structures in the lightcurve to within the signal-to-noise ratio of the data.  MGS will advise students in the writeup of the paper(s), authored and/or coauthored by students.
